### 2015-04-12 src/paper1/p1_results.tex
Fixed reference

To further validate the model, we independently tested one of its predictions that can be assessed experimentally in isolation: head-on-body variance. In supine position, subjects judged their head orientation (CW/CCW) relative to the body midline after it had been passively roll-rotated with speeds subthreshold for the canals to various angles (see \nameref{sec:methods}, Model validation: independent test of neck noise). Psychometric fits indicate no systematic bias in these head-on-body percepts (data not shown). Figure \ref{p1:fig6} depicts the experimental noise levels derived from these psychometric fits and the predicted values provided by the model, including their 95\% confidence intervals. Because the variance of the estimates increases with the average head-on-body percept, we performed a regression on the log-transformed data \cite{hopkins2000}. The significant correlation between predicted and measured neck noise levels (slope, 1.03; intercept, -0.1; $p = 0.04$) provides an independent confirmation of the proposed model.

>>>>

To further validate the model, we independently tested one of its predictions that can be assessed experimentally in isolation: head-on-body variance. In supine position, subjects judged their head orientation (CW/CCW) relative to the body midline after it had been passively roll-rotated with speeds subthreshold for the canals to various angles (see \nameref{p1:sec:methods}, Model validation: independent test of neck noise). Psychometric fits indicate no systematic bias in these head-on-body percepts (data not shown). Figure \ref{p1:fig6} depicts the experimental noise levels derived from these psychometric fits and the predicted values provided by the model, including their 95\% confidence intervals. Because the variance of the estimates increases with the average head-on-body percept, we performed a regression on the log-transformed data \cite{hopkins2000}. The significant correlation between predicted and measured neck noise levels (slope, 1.03; intercept, -0.1; $p = 0.04$) provides an independent confirmation of the proposed model.
